---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# causnet

<!-- badges: start -->
[![Codecov test coverage](https://codecov.io/gh/USCbiostats/causnet/branch/master/graph/badge.svg)](https://codecov.io/gh/USCbiostats/causnet?branch=master)
[![R build status](https://github.com/USCbiostats/causnet/workflows/R-CMD-check/badge.svg)](https://github.com/USCbiostats/causnet/actions)
<!-- badges: end -->

The goal of causnet is to find a globally optimal causal network given some data.

## Installation

You can install the development version from GitHub with:

```{r installation, eval=FALSE}
require("devtools")
install_github("USCbiostats/causnet")
```


~You can install the released version of causnet from [CRAN](https://CRAN.R-project.org) with:~

``` r
install.packages("causnet")
```

## Example

```{r}
library(causnet)

# simulate data
set.seed(1234)
mydata <- simdat(n_var = 5)

# causnet results
links.s <- causnet(mydata)

links.s
```

## Code of Conduct
  
  Please note that the causnet project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/1/0/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.

