---
title: "How to use the score_fun argument"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{score_fun-argument}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(causnet)
set.seed(1234)
```

`causnet()` can be run without setting the argument `score_fun`. In that case `causnet:::score_bic_lm` is used as the default.

```{r}
mydata <- simdat(n_var = 5)
causnet(data = mydata, max_parents = 3)
```

The Default scoring function is `score_bic_lm()` which is formulated as follows: 

```{r}
score_bic_lm <- function(y, x, mydat) {
  y_nm <- colnames(mydat)[y]
  if (is.element(x[1], seq_len(ncol(mydat)))) {
    x_nms <- colnames(mydat)[x]
  } else {
    x_nms <- "1"
  }
  fit <- lm(paste0(y_nm, " ~ ", paste(x_nms, collapse = " + ")), data = mydat)
  bic <- - (1 / 2) * BIC(fit)
  return(bic)
}
```

If you want to specify your own scoring you need to create a function that takes 3 arguments and returns a single numeric. Bigger values are better score for node y and parents x.

The first argument is passed in will be a single integer denoting the index of the response variable in the data. The second argument is a vector of integer denoting the dependant variables. Note that this can be `NA` if there are not dependant variables.
And the last argument is the `data`.

Suppose we want a score function that gives back the average correlation between `y` and `x`. 
This score function can be written as follows. Notice that we are handling the special case where `x = NA`.
```{r}
mean_cor_score <- function(y, x, mydat) {
  if (any(is.na(x))) return(0)
  
  mean(cor(mydat[x], mydat[y]))
}
```

Now we simply pass our custom scoring function to `score_fun` and run

```{r}
causnet(data = mydata, max_parents = 3, score_fun = mean_cor_score)
```

